% No previous versions yet.  

% these would be subsections "Changes from v. WD-..."
% Use itemize environments.
% ------------------------------------
%\subsection{Changes from WD-YYYY-MM-DD}
%\begin{itemize}
%\item Add Change List
%\end{itemize}
% ------------------------------------

\subsection{Changes from initial draft WD-2014-06-13}
\begin{itemize} % 2014 Sep 30:
  \item  Draft revised with STC2 prototype, initial draft feedback, and updates due to Cube model development.
\end{itemize}

\subsection{Changes from WD-2014-09-30}
\begin{itemize} % 2015 Mar 02
  \item Incorporate comments from Spectral2.0 feedback related to Dataset metadata.
  \item Format change to better illustrate data type and multiplicity of elements.
  \item Update STC2 prototype to current state of development.
  \item General review of element descriptions for clarity.
\end{itemize}

\subsection{Changes from WD-2015-03-02}
\begin{itemize} % 2015 Oct 07
  \item Update Acknowledgments for European contributors
  \item Generalize Derived object using ObsConfig pattern
  \item Remove Redshift type (used in Derived)
  \item Update STC2 prototype to 2015-05-04 model descriptions (except for Transform model)
  \item Update reference to VO-DML specification (2015-02-06 version) - Make section references links.
\end{itemize}

\subsection{Changes from WD-2015-10-07}
\begin{itemize} % 2015 Oct 18
  \item Update STC2 prototype to 2015-10-14 model diagrams
  \begin{itemize}
    \item Frame - Transform relation. 2016 Mar 09:
  \end{itemize}
  \item Update elements for vo-dml compatibility
  \begin{itemize}
    \item Curation.reference, DataID.collection, DataID.contributor o Enumerations (SpectralBandType)
  \end{itemize}
  \item Added simple Party model for Entity types
  \begin{itemize}
    \item Curation.publisher, Curation.contact, DataID.creator, DataID.contributor
  \end{itemize}
  \item Restructured ObsConfig, folding in content concepts, not just content. - Normalized Curation.rights from string to AccessRights type.
  \item Update STC2 prototype
  \begin{itemize}
    \item duplicate packaging
    \item mods for vo-dml compliance, PixelSpace, PixelCoordinate, Transforms. 2016 Apr 12:
  \end{itemize}
  \item restore Curation.rights to attribute of type RightsType, delete AccessRights type.
  \item reduce Party types to just Organization and Individual.
  \item enhanced language in Publication.refCode description.
  \item moved ObsDataset and associated elements to Observation-Experiment package - added list of figures
\end{itemize}

\subsection{Changes from WD-2015-10-18}
\begin{itemize} % 2016 Oct 31
  \item remove STC2 prototype model
\end{itemize}

%\subsection{Changes from WD-2016-10-31}
\begin{itemize} % 2017 Sep 27
  \item removed Characterisation element from ObsDataset; belongs on specific dataset types.
  \item removed CoordSys element from ObsDataset; convenience element for content defined elsewhere.
  \item update to current STC2 Measurement model interface
\end{itemize}

\subsection{Changes from WD-2017-09-27}
\begin{itemize} % 2019 Sep 17
  \item update to Measurements model (minor); and stereotype URLs.
\end{itemize}

\subsection{Changes from WD-2019-09-17}
\begin{itemize} % 2022 Dec 13
  \item migration to ivoatex
\end{itemize}

